Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2015-04-07 tese/section01.tex
[ADD] added more references, a simple paragraph about skype

Compared to Skype, \ac{WebRTC} allows web browser real time communications without installing any aditional application or plugin.

>>>>

{\color{blue}Skype is a stand-alone application which is compatible with all major operating systems (Windows, Linux, MacOS) and mobile operating systems (Android, iOS, Windows). This enables voice, IM and video communication. It's main advantage is that it has a huge installation base (approx 299 million users).}

Compared to Skype, \ac{WebRTC} is an open source technology that allows web browser real time communications without installing any aditional application or plugin.

### 2015-04-07 tese/section02.tex
[ADD] added more references, a simple paragraph about skype

  WebSockets provide bidirectional communications trough a full-duplex socket channel. WebSocket handshake phase specifies an \ac{HTTP} header in order to upgrade to websocket type of communication, the remainder messages are done without \ac{HTTP} headers, which leads to much smaller messages and better network usage. WebSockets may not be avalailable on every web browser, frameworks like \textit{socket.io}\footnote{\url{http://socket.io/}} and \textit{SockJS}\footnote{\url{http://github.com/sockjs}} uses \ac{HTTP} when there is no support for WebSockets.

@@

  \ac{SIP} is protocol used for negotiation, creation, modification and finalization of communication sessions between users. \ac{SIP} follows a client/server architecture with \ac{HTTP} like messages and it can be used as signaling protocol. The advantage of \ac{SIP} is the ability to make video and voice calls applications over \ac{IP} networks.

>>>>

  The WebSocket protocol (rfc6455\footnote{\url{http://tools.ietf.org/html/rfc6455}}) provides bidirectional communications trough a full-duplex socket channel. WebSocket handshake phase specifies an \ac{HTTP} header in order to upgrade to websocket type of communication, the remainder messages are done without \ac{HTTP} headers, which leads to much smaller messages and better network usage. WebSockets may not be avalailable on every web browser, frameworks like \textit{socket.io}\footnote{\url{http://socket.io/}} and \textit{SockJS}\footnote{\url{http://github.com/sockjs}} uses \ac{HTTP} when there is no support for WebSockets.

@@

  \ac{SIP} (rfc3261\footnote{\url{http://tools.ietf.org/html/rfc3261}}) is protocol used for negotiation, creation, modification and finalization of communication sessions between users. \ac{SIP} follows a client/server architecture with \ac{HTTP} like messages and it can be used as signaling protocol. The advantage of \ac{SIP} is the ability to make video and voice calls applications over \ac{IP} networks.
